CS246: Twitter Purification

### 2014-06-08 Paper.tex
Adding refs

\section*{Related work}
\paragraph{} Aspell's algorithm uses a combination of DoubleMetaphone and weighted edit distance to find correction candidates.\footnote{\href{http://aspell.net/0.50-doc/man-html/8_How.html}{8. How Aspell Works}} Search engines such as Google use a more similar method to what was outlined here, using a combination of probabilistic data and edit distance.
Subhabrata Mukherjee, etc published a paper that dealt with sentiment analysis of tweets. In their pre-processing work, they used a Twitter specific spellchecking algorithm, which utilized vowel exchange, dropping of vowels, text compression, squeeze, and edit distance methods. They had intended to also deal with phonetic transformation, segmentation with punctuation, segmentation with compound words, etc.

@@

\section*{References}

\end{document}

>>>>

\section*{Related work}
\paragraph{} Aspell's algorithm uses a combination of DoubleMetaphone and weighted edit distance to find correction candidates.\footnote{\href{http://aspell.net/0.50-doc/man-html/8_How.html}{8. How Aspell Works}} Search engines such as Google use a more similar method to what was outlined here, using a combination of probabilistic data and edit distance.
Subhabrata Mukherjee et al published a paper that dealt with sentiment analysis of tweets. In their pre-processing work, they used a Twitter specific spellchecking algorithm, which utilized vowel exchange, dropping of vowels, text compression, squeeze, and edit distance methods. They had intended to also deal with phonetic transformation, segmentation with punctuation, segmentation with compound words, etc.

@@

\section*{References}
\footnotesize{
\paragraph{}Subhabrata Mukherjee, Akshat Malu, Balamurali A.R., and Pushpak Bhattacharyya. 2012. ``TwiSent: a multistage system for analyzing sentiment in twitter.'' \textit{Proceedings of the 21st ACM international conference on Information and knowledge management} (CIKM '12). ACM, New York, NY, USA, 2531-2534. DOI=10.1145/2396761.2398684 http://doi.acm.org/10.1145/2396761.2398684

\paragraph{} Angell, Richard C., George E. Freund, and Peter Willett. ``Automatic spelling correction using a trigram similarity measure.'' \textit{Information Processing \& Management} 19.4 (1983): 255-261.

}
\end{document}
